---
title: "Descriptive Statistics Assignment"
author: "Anastasia Vorontsova"
output:
  html_notebook:
    theme: lumen
  html_document:
    df_print: paged
---

#Your turn!
We went through some exploratory analysis on our own, which will help us answer some questions in the data, and will actually give us more questions! Now pick another dataset from `mlbench` and create a markdown notebook of you exploring the data, following the same 5 steps.

1. Take a glimpse at your data
2. Look at the dimensions of your data
3. Look at the class types of your data
4. Distribution of your data
5. Correlations in your data
---

Load mlbench and tidyverse
```{r}
#code to load
```
The package `mlbench` has a bunch of datasets that you can use to explore and build machine learning models on. 

Select the dataset you'll work with and load it using `data()`
```{r}
data(jasa)

```

> Since we aren't familiar with the variables in this data, we should probably keep the explanation of these variables handy

## Explore!
1. **Take a glimpse of your data.**
```{r}
head(jasa)

```
```{r}
tail(jasa)
```


2. **Look at the dimensions of your data.**
```{r}
dim(jasa)
```   
    
3. **Look at the class types of each variable in your data.**
```{r}
str(jasa)
```
4. **Distribution of your data**
```{r}
summary(jasa)
```
```{r}
describe(jasa)
```



5. **Correlations in your data**

```{r}
jasa_explore <- subset.data.frame(jasa, select = c(fustat, age, surgery, futime))
                  
correlations <- cor(jasa_explore)
corrplot(correlations, method = "circle")

```

-> The sooner is the follow up after the heart transplant surgery, the higher is the chance that the patinet survives.
